Low-lying collective excited states in non-integrable system based on stationary phase approximation to the path integral

### 2018-09-21 paper2/draft1-1.tex
draft1.1

Due to $J$ is conserved quantity, the action integral can be divided into two terms
\begin{align}
  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
\end{align}
where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
\begin{align}
  \mathcal{T}_{\rm intr}(t) &= \int \braket{J;q,p|i\frac{\partial}{\partial t}|J;q,p} dt
	 \nonumber \\
	&= \int \sum_l j_l d\chi_l .
	\label{tau}
\end{align}
The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
In SU(2) representation, the invariant measure is
\begin{align}
  d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi} (1+|Z_l|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
 =& \prod_l \frac{\Omega_l+1}{4\pi} d \cos{\theta_l} d\chi_l \nonumber \\
 =& \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} d\chi_l dj_l \nonumber \\
 =& \left[ \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} \right] d\Phi dJ dqdp \nonumber \\
 &\times dQ_1\cdots dQ_{l-2}dP_1\cdots dP_{l-2}
% d\Phi dJ dq dp = d\Phi dJ dE dt 
\end{align}
where $(Q_i,P_i)$ are the other canonical variables decoupled from the collective coordinates. From the third line to the forth line, we used that Jacobian equals one in canonical transformation. The part of the invariant measure which contributes to the excited states is
\begin{align}
d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
\end{align}
Under EBK quantization condition (\ref{EBK}),
the $k$-th excited state becomes
\begin{align}
 \ket{\tilde{\phi}_k} \propto& \oint d\Phi \oint dt \ket{\Phi,J;q,p} e^{i\mathcal{T}(\Phi,J;q,p)}
 \nonumber \\
 =& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \nonumber \\
 &\times \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+j_l,\cdots} \nonumber \\
 \equiv& \sum_{\{j_l\}\in (\sum_{j_l}=J)} C_{j_l} \ket{\cdots;S_l,-S_l+j_l,\cdots}
\end{align}
where
\begin{align}
  C_{j_l} = \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q(t),p(t)).
  \label{coef}
\end{align}

@@

Based on the information from ASCC calculation, we can obtain the excited states from SPA.
Table \ref{ex} shows the excitation energies of first and second excited states in the collective subspace. Up to the second excitation, all of the energies are in their energy pockets shown in Fig. \ref{potential}. Compare the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced. The slightly difference is that the values from ASCC+SPA are about $5\%$ smaller than exact solution. 
\begin{table}[htbp]
\begin{ruledtabular}
\begin{tabular}{c|c|cccccc}
            & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
$0_2^+$ one & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
phonon &ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
$0_4^+$ two & Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
phonon &ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
\end{tabular}
\end{ruledtabular}
\caption{Excitation energies of one-phonon and two-phonon states from exact solution and ASCC+SPA calculation. In a chosen collective subspace, one-phonon and two-phonon states correspond to the first and second excitation, respectively. In the whole Hilbert space, one-phonon and two-phonon states correspond to $\ket{0_2^+}$ and $\ket{0_4^+}$, respectively.}
\label{ex}
\end{table}

@@

\subsection{Realistic single-particle level system}

@@

\begin{table}[htbp]
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
 Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$\\
ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
\end{tabular}
\end{ruledtabular}
\caption{The same as Fig. \ref{ex} but for Pb isotopes.}
\label{Pb_ex}
\end{table}

>>>>

Due to $J$ is conserved quantity, the action integral can be divided into two terms
\begin{align}
  \mathcal{T}(\Phi,J;q,p) &= \mathcal{T}_{\rm intr}(t) + J\Phi, 
\end{align}
where the intrinsic action integral $\mathcal{T}_{\rm intr}(t)$ becomes
\begin{align}
  \mathcal{T}_{\rm intr}(t) &= \int \braket{J;q,p|i\frac{\partial}{\partial t}|J;q,p} dt
	 \nonumber \\
	&= \int \sum_l j_l d\chi_l .
	\label{tau}
\end{align}
The important point is $\mathcal{T}_{\rm intr}(t) \ne \int p dq$ at each $t$. For closed TDHFB trajectory, only $\mathcal{T}_{\rm intr}(t)$ contributes to the excited states.
In SU(2) representation, the invariant measure is
\begin{align}
  d\mu(Z) &= \prod_l \frac{\Omega_l+1}{\pi} (1+|Z_l|^2)^{-2} d{\rm Re}Z d{\rm Im}Z \nonumber \\
 =& \prod_l \frac{\Omega_l+1}{4\pi} d \cos{\theta_l} d\chi_l \nonumber \\
 =& \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} d\chi_l dj_l \nonumber \\
 =& \left[ \prod_l \frac{-(1+\Omega_l^{-1})}{2\pi} \right] d\Phi dJ dqdp \nonumber \\
 &\times dQ_1\cdots dQ_{l-2}dP_1\cdots dP_{l-2}
% d\Phi dJ dq dp = d\Phi dJ dE dt 
\end{align}
where $(Q_i,P_i)$ are the other canonical variables decoupled from the collective coordinates. From the third line to the forth line, we used that Jacobian equals one in canonical transformation. The part of the invariant measure which contributes to the excited states is
\begin{align}
d\mu(\Phi,J;q,p) \propto d\Phi dJ dqdp = d\Phi dJ dE dt. 
\end{align}
Under EBK quantization condition (\ref{EBK}),
the $k$-th excited state becomes
\begin{align}
 \ket{\tilde{\phi}_k} \propto& \oint d\Phi \oint dt \ket{\Phi,J;q,p} e^{i\mathcal{T}(\Phi,J;q,p)}
 \nonumber \\
 =& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \nonumber \\
 &\times \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q,p) \ket{\cdots;S_l,-S_l+j_l,\cdots} \nonumber \\
 \equiv& \sum_{\{j_l\}\in (\sum_{j_l}=J)} C_{j_l} \ket{\cdots;S_l,-S_l+j_l,\cdots}
 \label{SPA2}
\end{align}
where
\begin{align}
  C_{j_l} = \oint dt e^{i\mathcal{T}_{\rm intr}(t)} A_{j_l}(q(t),p(t)).
  \label{coef}
\end{align}

The definition of wave function in SPA can also be extended into ground state. The ground state is constructed by only energy minimum point in TDHFB phase space. In the energy minimum point, $\ket{\Phi,J;q,p}=\ket{\rm HFB}$. Therefore, (\ref{SPA2}) becomes
\begin{align}
 \ket{\tilde{\phi}_{g.s.}} \propto& \sum_{\{j_l\}} \oint d\Phi e^{i(J-\sum_l j_l)\Phi} \ket{\rm HFB},  
\end{align}
which is identical to the wave function of the particle number projection for HFB state.

@@

Based on the information from ASCC calculation, we can obtain the excited states from SPA.
Table \ref{ex} shows the excitation energies of first and second excited states in the collective subspace. Up to the second excitation, all of the energies are in their energy pockets shown in Fig. \ref{potential}. Comparing the result from ASCC+SPA with exact solution, we can find all of the values are nicely reproduced. The slightly difference is that the values from ASCC+SPA are about $5\%$ smaller than exact solution. 
Using the wave function of excited states, the pair additional transition strength is shown in Fig. \ref{3levelPad}. For intraband transition, comparing ASCC+SPA with exact solution, $B(P_{\rm ad};0\rightarrow 0)$ are almost identical and $B(P_{\rm ad};1\rightarrow 1)$ are about $10\%\sim20\%$ small. 
For interband transition, the strength from ASCC+SPA is much smaller than exact solution. However, because the pairing correlation is enough strong in this case, the strength of intraband transition is dominant compared with interband transition. We can find that $B(P_{\rm ad};0\rightarrow 1)$ and $B(P_{\rm ad};1\rightarrow 0)$ are only about $1\%$ of $B(P_{\rm ad};0\rightarrow 0)$ and $B(P_{\rm ad};1\rightarrow 1)$. Therefore, the interband transition can be regarded as reasonable. From all above results, we can conclude that ASCC+SPA reproduces exact solution quantitatively. 
\begin{table}[htbp]
\begin{ruledtabular}
\begin{tabular}{c|c|cccccc}
            & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
$0_2^+$ one & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
phonon &ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
$0_4^+$ two & Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
phonon &ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.92$ & $8.26$ & $8.47$\\
\end{tabular}
\end{ruledtabular}
\caption{Excitation energies of one-phonon and two-phonon states from exact solution and ASCC+SPA calculation. In a chosen collective subspace, one-phonon and two-phonon states correspond to the first and second excitation, respectively. In the whole Hilbert space, one-phonon and two-phonon states correspond to $\ket{0_2^+}$ and $\ket{0_4^+}$, respectively.}
\label{ex}
\end{table}

@@

\subsection{Pb isotopes}
With pairing model, we study neutron's pairing vibration in Pb isotope. We prepare the neutron's single-particle level between the magic number 82 and 126 (Table \ref{Pb}). The coupling constant $g=0.138$ is determined to reproduce the experimental pairing gap $\Delta(N)=\frac{(-1)^{N+1}}{2}(B(N+1)-2B(N)+B(N-1))$ of ${}^{192}$Pb. We consider the even-even system from ${}^{188}$Pb to ${}^{194}$Pb.
\begin{table}[htbp]
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
  orbit& $h_{9/2}$ & $f_{7/2}$ & $i_{13/2}$ & $p_{3/2}$ & $f_{5/2}$ & $p_{1/2}$\\ \hline
  energy& $-10.94$ & $-10.69$ & $-8.74$ & $-8.44$ & $-8.16$ & $-7.45$\\
\end{tabular}
\end{ruledtabular}
\caption{Single-particle levels of Pb isotopes used in the calculation. The orbits are obtained from spherical Woods-Saxon potential with spin-orbit coupling. }
\label{Pb}
\end{table}

We have six TDHFB degrees of freedom in the system. Fig. \ref{Pb_omega_sq} shows the eigenvalue of moving-frame QRPA equation. We can find there are one spurious mode and five vibrational modes. Even though the degrees of freedom increase compared with three-level system, the collective modes we focus on did not cross with other modes in all panels. It means that the collective mode is nicely decoupled from other degrees of freedom. Under the chosen mode, the occupation number is shown in Fig. \ref{Pb_occ_number}. As with three-level system, the left end points correspond to HF state in all panels. The last neutrons are in $i_{13/2}$ from ${}^{188}$Pb to ${}^{194}$Pb. In the collective path, we can find $i_{13/2}$ and $p_{3/2}$ changes significantly, while other orbits are almost constant.

@@

\begin{table}[htbp]
\begin{ruledtabular}
\begin{tabular}{c|cccccc}
   & ${}^{186}$Pb & ${}^{188}$Pb & ${}^{190}$Pb & ${}^{192}$Pb & ${}^{194}$Pb & ${}^{196}$Pb\\ \hline
 Exact & $2.58$ & $2.44$ & $2.34$ & $2.25$ & $2.20$ & $2.15$\\
ASCC+SPA & unbound & $2.31$ & $2.21$ & $2.12$ & $2.04$ & unbound \\ 
\end{tabular}
\end{ruledtabular}
\caption{The same as Table. \ref{ex} but for Pb isotopes.}
\label{Pb_ex}
\end{table}
